Binary companions of red clump stars

### 2017-08-05 paper/main.tex
parameter names and definitions

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.
% - Make sure that two assumptions in the two assumption lists only have the same name if they really are the same assumption: These are proper names!
% - Hyphenate binary-star when it is an adjective, not when it is a noun!

@@

@@

In addition to the above requirements, we make the following assumptions
that restrict our attention to a well-defined model space:
\begin{description}
\item[correct samplings] accurate representations of posterior pdf
  given prior and likelihood; correct likelihood function. We hereby
  take on all the assumptions given in \sectionname~\ref{sec:fitting},
  about noise and kinematics, and so on.
\item[no trinaries] related to the above: no trinaries, quads, or anything
  crazier.
\item[sufficent samplings] density and support of samplings
\item[independent stars] no relation between one star and another; each
  drawn from the same population; no multiple populations.
\item[masses known] The mass of each primary \RC\ star is known, with
  a correctly known posterior pdf, from prior work (CITE NESS).
\item[population parameterization] We adopt the following
  parameterization of the population. In what follows, $\theta$ will
  stand in for the full set of hyper-parameters (population
  parameters).
  \begin{itemize}
  \item Each primary \RC\ star has a probability $F$ (pure probability
    $0<F<1$) of having a secondary companion. $F$ is a hyper-parameter
    in $\theta$.
  \item The log-period distribution $p(\ln P\given\theta)$ is a power
    law between end-points, or
    \begin{eqnarray}
      \ln p(\ln P\given\theta) &=& g_0 + (g_1 - g_0)\,\frac{\ln P - x_0}{x_1 - x_0}
      \quad \mbox{for $x_0<\ln P<x_1$,}
    \end{eqnarray}
    where $g_0, g_1, x_0, x_1$ are hyper-parameters in $\theta$.
  \item Each primary star has a true mass $M$ (which we only know
    noisily) and the companion mass is potentially larger or
    smaller (!). The log-mass-ratio distribution $p(\ln q\given\theta)$ is
    \begin{eqnarray}
      \ln p(\ln q\given\theta) &=& h_0 + (h_1 - h_0)\,\frac{\ln q - y_0}{y_1 - y_0}
      \quad \mbox{for $y_0<\ln q<y_1$,}
    \end{eqnarray}
    where $h_0, h_1, y_0, y_1$ are hyper-parameters in $\theta$.
  \item The eccentricity distribution $p(e\given P,\theta)$ is a beta,
    and permitted to vary with period:
    \begin{eqnarray}
      p(e\given P,\theta) &=& B(e\given \alpha(P),\beta(P))
      \\
      \alpha(P) &=& a_0 + (a_1 - a_0)\,\frac{P - x_0}{x_1 - x_0}
      \\
      \beta(P) &=& b_0 + (b_1 - b_0)\,\frac{P - x_0}{x_1 - x_0}
      \quad ,
    \end{eqnarray}
    where $B(x\given\alpha,\beta)$ is the beta distribution with
    control parameters $\alpha,\beta$, and $a_0, a_1, b_0, b_1$ are
    hyper-parameters in $\theta$.
  \item The inclination distribution $p(i)$ and the argument-of-perihelion
    distribution $p(\omega)$ and the phase distribution $p(\phi)$ are all
    fixed to their isotropic distributions. They bring no hyper-parameters
    to $\theta$.
  \end{itemize}
\item[hyper-priors] whatevs
\end{description}

@@

Because all we have is a sampling of each system under the interim prior
$p(\omega\given H_0)$,
we have to re-weight or importance-sample the individual-star samplings
in this hierarchical inference... Cite Hogg et al; Cite DFM et al.
% The following needs checking for symbol conventions
\begin{eqnarray}
  \ln p(y\given\alpha,H_1) &=& \sum_{n=1}^N \ln p(y_n\given\alpha,H_1)
  \\
  \ln p(y_n\given\alpha,H_1) &\propto& \ln\left[\frac{1}{K_n}\,\sum_{k=1}^{K_n}\frac{p(\omega_{nk}\given\alpha,H_1)}{p(\omega_{nk}\given H_0)}\right]
  \quad .
\end{eqnarray}

>>>>

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.
% - Make sure that two assumptions in the two assumption lists only have the same name if they really are the same assumption: These are proper names!
% - Hyphenate binary-star when it is an adjective, not when it is a noun!
% - Where there are defined math symbols (like \pars), use them!

@@

% define macros for math
\newcommand{\hyperpars}{\gamma}
\newcommand{\pars}{\theta}

@@

In addition to the above requirements, we make the following assumptions
that restrict our attention to a well-defined model space:
\begin{description}
\item[correct samplings] accurate representations of posterior pdf
  given prior and likelihood; correct likelihood function. We hereby
  take on all the assumptions given in \sectionname~\ref{sec:fitting},
  about noise and kinematics, and so on.
\item[no trinaries] related to the above: no trinaries, quads, or anything
  crazier.
\item[sufficent samplings] density and support of samplings
\item[independent stars] no relation between one star and another; each
  drawn from the same population; no multiple populations.
\item[masses known] The mass of each primary \RC\ star is known, with
  a correctly known posterior pdf, from prior work (CITE NESS).
\item[population parameterization] We adopt the following
  parameterization of the population. In what follows, $\hyperpars$ will
  stand in for the full set of hyper-parameters (population
  parameters).
  \begin{itemize}
  \item Each primary \RC\ star has a probability $F$ (pure probability
    $0<F<1$) of having a secondary companion. $F$ is a hyper-parameter
    in $\hyperpars$.
  \item For those with secondary companions, the log-period $\ln P$
    distribution $p(\ln P\given\hyperpars)$ is a power law between
    end-points, or
    \begin{eqnarray}
      \ln p(\ln P\given\hyperpars) &=& g_0 + (g_1 - g_0)\,\frac{\ln P - x_0}{x_1 - x_0}
      \quad \mbox{for $x_0<\ln P<x_1$,}
    \end{eqnarray}
    where $g_0, g_1, x_0, x_1$ are hyper-parameters in $\hyperpars$.
    Parameters $g_0, g_1$ are natural logs of densities in log-period space.
    Parameters $x_0, x_1$ are log-period limits.
  \item Each primary star has a true mass $M$ (which we only know
    noisily) and the companion mass is potentially larger or
    smaller (!). The log-mass-ratio $\ln q$ distribution
    $p(\ln q\given\hyperpars)$ is
    \begin{eqnarray}
      \ln p(\ln q\given\hyperpars) &=& h_0 + (h_1 - h_0)\,\frac{\ln q - y_0}{y_1 - y_0}
      \quad \mbox{for $y_0<\ln q<y_1$,}
    \end{eqnarray}
    where $h_0, h_1, y_0, y_1$ are hyper-parameters in $\hyperpars$.
    Parameters $h_0, h_1$ are natural logs of densities in log-mass-ratio space.
    Parameters $y_0, y_1$ are log-mass-ratio limits.
  \item The eccentricity distribution $p(e\given P,\hyperpars)$ is a beta,
    and permitted to vary with period:
    \begin{eqnarray}
      p(e\given P,\hyperpars) &=& B(e\given \alpha(P),\beta(P))
      \\
      \alpha(P) &=& a_0 + (a_1 - a_0)\,\frac{P - x_0}{x_1 - x_0}
      \\
      \beta(P) &=& b_0 + (b_1 - b_0)\,\frac{P - x_0}{x_1 - x_0}
      \quad ,
    \end{eqnarray}
    where $B(x\given\alpha,\beta)$ is the beta distribution with
    control parameters $\alpha,\beta$, and $a_0, a_1, b_0, b_1$ are
    hyper-parameters in $\hyperpars$.
    Parameters $a_0, a_1$ are values of the beta-distribution alpha-parameter
    at the log-period limits, and parameters $b_0, b_1$ are values of the
    beta-distribution beta-parameter at the limits.
  \item The inclination $i$ distribution $p(i)$ and the
    argument-of-perihelion $\omega$ distribution $p(\omega)$ and the
    orbital-phase $\phi$ (at the fiducial time DEFINE THIS)
    distribution $p(\phi)$ are all fixed to their isotropic
    distributions. They bring no hyper-parameters to $\hyperpars$.
  \end{itemize}
\item[hyper-priors] whatevs
\end{description}

@@

Because all we have is a sampling of each system under the interim prior
$p(\pars\given H_0)$,
we have to re-weight or importance-sample the individual-star samplings
in this hierarchical inference... Cite Hogg et al; Cite DFM et al.
% The following needs checking for symbol conventions
\begin{eqnarray}
  \ln p(y\given\hyperpars,H_1) &=& \sum_{n=1}^N \ln p(y_n\given\hyperpars,H_1)
  \\
  \ln p(y_n\given\hyperpars,H_1) &=& \ln\left[\frac{1}{K_n}\,\sum_{k=1}^{K_n}\frac{p(\pars_{nk}\given\hyperpars,H_1)}{p(\pars_{nk}\given H_0)}\right] + Q_n
  \quad ,
\end{eqnarray}
where $y$ is the full data set, $y_n$ is the data set for star $n$,
$\hyperpars$ is the vector of hyper-parameters,
$H_1$ is the hypothesis (or model) that is our
hyper-parameter-controlled hierarchical model,
$H_0$ is the hypothesis corresponding to the interim prior of \sectionname~\ref{sec:fitting},
the $\pars_{nk}$ are, for each star $n$, the $K_n$ samples from
the posterior under $H_0$ (the interim prior),
and $Q_n$ is an arbitrary constant that does not depend on any of the
hyper-parameters.
